%!TEX TS-program = xelatex
\documentclass{friggeri-cv}
\addbibresource{bibliography.bib}

\usepackage{ulem}


\begin{document}
\header{Guilherme}{Nogueira}
       {software developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    R. Ministro Gastão Mesquita, 257
    05012-010 São Paulo
    Brasil
    ~
    +55 11 9 8393 2639
    %+33 \phantom{0}7 53 05 52 36
    {\footnotesize skype} guilherme\_nirev
    \href{mailto:guilherme@nirev.org}{guilherme@nirev.org}
    \href{http://nirev.org}{http://nirev.org}
  \section{languages}
    native portuguese
    fluent english
    basic french
  \section{programming}
    Java, Ruby, Javascript, C, Python,
    HTML, css, bash, PHP
  \section{skills/tools}
    mysql, postgres,
    nginx, chef, docker, DevOps,
    shell scripting
  \section{interests}
distributed systems, p2p, mobile apps, data structures, music, martial arts, science fiction books
\end{aside}


\section{education}

\begin{entrylist}

\entry
  {2011–2014}
  {Master in Computer Science}
  {University of São Paulo - Brazil}{}
\entry
  {2005–2010}
  {B.Sc. in Computer Science}
  {Universidade Federal do Espírito Santo - Brazil}{}
\end{entrylist}

\section{experience}

\workentry
  {November 2012}{*}
  {Software Craftsman at Elo7}
  {São Paulo - Brazil}
  {Our platform has high traffic and transaction volume. Our stack is based on Java, Ruby and Scala and infrastructure
  is on AWS. A fast paced environment, following agile practices, and focusing on delivering fast with quality. We
  measure and log everything with StatsD, Graphite, and NewRelic. We deploy constantly. I work in the Search Team using
  Solr and other tools written in Java and Ruby, I deal with vanilla Javascript and SASS on frontend, as long maintaining our infrastructure and pipeline tools.}

\workentry
  {April 2012}{October 2012}
  {Undergraduate Intern at INRIA Paris-Roquencourt}
  {Rocquencourt, Île-de-France - France}
  {Research on supporting non-functional requirements for Wireless Sensor Networks macroprogramming using SunSPOTs.}

\workentry
  {March 2011}{September 2012}
  {Undergraduate Researcher for CHOReOS project}
  {University of São Paulo, São Paulo - Brazil}
  {Research and implementation involving: choreography analysis using graph metrics,
  dynamic adaptation techniques, implementation of a testing framework, and cloud computing.}

\workentry
  {August 2010}{February 2011}
  {Software Developer/Analyst at RR Sistema}
  {Vitória/ES - Brazil}
  {Porting their implementation of Brazilian DTV middleware to different platforms.
  Mainly programming in C/C++, with low-level and multimedia libraries (GStreamer, DirectFB, pthreads, osal, etc),
  and required knowledge of the Brazilian digital television standards, Linux, embedded systems and
  distributed version control systems.}

\workentry
  {January 2009}{December 2010}
  {Undergraduate Intern at Multimedia and Network Research Lab}
  {Federal Univ. of Espiríto Santo, Vitória/ES - Brazil}
  {Working with the Brazilian DTV middleware; ported it for Android. }

\workentry
  {August 2008}{December 2008}
  {Undergraduate Intern at Laboratory of Advanced Software SYstems (LASSY)}
  {University of Luxembourg - Luxembourg}
  {Worked in the RESIST project, developing a prototype for an eHealth application using SOA with multiple Web Services,
  using standards such as Apache CXF and WS-Security.}

% \workentry
%   {January 2008}{March 2008}
%   {Intern at CISA Trading S.A.}
%   {Trading company, São Paulo/SP - Brazil}
%   {Maintaining their internal software solution which manages all of the companies processes.
%   The system was written in the Progress4GL language.}

\workentry
  {March 2007}{December 2007}
  {Undergraduate Intern at NINFA laboratory}
  {Federal University of Espiríto Santo, Vitória/ES - Brazil}
  {Joint project with ESCELSA, state's electric power utility, building automated classifiers
  for finding frauds done by its clients. Used optimization heuristics, neural networks and clustering.
  Tools developed in Java, C++ and Matlab.}

\workentry
  {September 2006}{March 2007}
  {PHP Developer at Lettera Soluções}
  {Web developing company, Vitória/ES - Brazil}
  {Developing and managing web sites using CSS, (x)HTML, PHP, ASP, MySQL, PostgreSQL, as well as common Linux admin tools.}

\printbibsection{article}{article in peer-reviewed journal}
\printbibsectionpar{inproceedings}{international peer-reviewed conferences/proceedings}{notkeyword={brazil}}
\printbibsectionpar{inproceedings}{local peer-reviewed conferences/proceedings}{keyword={brazil}}
\printbibsection{misc}{other publications}
\printbibsection{report}{research reports}

\end{document}
